EUC_PVE

### 2014-07-30 markdowns/master.rmd
added spot A measurement to MD
started sla no tnc markdown master script
uncommented master.rmd source()

@@

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r Amass vs TNC and N}
#source(("master_scripts/photochem_predict.R")
```

>>>>

asat and amax

```{r photosynthesis plotting}
source("master_scripts/A_plotting.R")
```

@@

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r Amass vs TNC and N}
source("master_scripts/photochem_predict.R")
```
